That’s a Big-Ass Chicken: Care and Management of Large Chicken Breeds for Optimal Health and Productivity

### 2025-03-02 Manuscript_Final.qmd
correct name
edit hen name and photo

> *If you've ever seen a picture of Eddy the Chicken, your first words would invariably be "That's a Big-Ass Chicken!" And you would be correct. See Figure 1 for reference.*

```{r, echo=FALSE}
#![Eddy the Chicken](sampleimage.png){
  #fig-myimportedimage 
 # width="5in" 
 # fig-alt="A picture of Eddy the Chicken being a Big-Ass Chicken on the shoulder of the first author's sister." 
 # apa-note="This is a Big-Ass Chicken."
 # }
```

>>>>

> *If you've ever seen a picture of Edgar the Chicken, your first words would invariably be "That's a Big-Ass Chicken!" And you would be correct. See Figure 1 for reference.*

```{r, echo=FALSE}
#![Edgar the Chicken](orpignton hen(edgar).jpg){
  #fig-myimportedimage 
 # width="5in" 
 # fig-alt="A picture of Eddy the Chicken being a Big-Ass Chicken on the shoulder of the first author's sister." 
 # apa-note="This is a Big-Ass Chicken."
 # }
```
